---
title: "Data Cleaning and Visualising"
author: "Jia Xin"
date: "3/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(googlesheets4)
library(janitor)
library(lubridate) # this package is part of tidyverse but not loaded by default
library(repurrrsive)
library(tools)

library(tmap)
library(sf)
library(geojsonsf)
library(ggmap)
library(mapview)

library(httr)
library(osmdata)
library(dplyr)
library(stringr)

library(forcats)
library(infer)
```

# Dormitory locations data 

## Loading dormitory locations data 
```{r}
dormitories <- read_csv("data/dormitories_cleaned.csv")
```

## Clean dormitory dataset 
```{r}
dormitories <- dormitories %>%
  filter (Dormitory != "NA")
```

```{r}
dormitories <- dormitories %>%
  clean_names()
```

```{r}
dormitories <- dormitories %>% 
mutate(dormitory = recode(dormitory,`Kian Teck Dormitory\n` = "Kian Teck Dormitory",`Kian Teck Hostel\n` = "Kian Teck Hostel",`Blue Stars Dormitory\n` = "Blue Stars Dormitory", `Jurong Apartments\n` = "Jurong Apartments", `Avery Lodge\n` = "Avery Lodge", `Cassia @ Penjuru\n` = "Cassia @ Penjuru")) %>%
  mutate (address_of_dormitory = recode (address_of_dormitory, `16 Tuas Avenue 1 #07-201 Singapore 639529` = "14 Tuas Ave 1, Singapore 639499"))
```

## Geocoding
```{r}
register_google(key = "AIzaSyD5QiSXsdezyH3ylxzOH43WOnQJOwgZxTM")

dormitories$lon <- NA
dormitories$lat <- NA
```

```{r}
# Loop through the addresses to get the latitude and longitude of each address and add it to the
# dormitories data frame in new columns lat and lon
for(i in 1:nrow(dormitories)) {
  result <- geocode(dormitories$address_of_dormitory[i], output = "latlona", source = "google")
  dormitories$lon[i] <- as.numeric(result[1])
  dormitories$lat[i] <- as.numeric(result[2])
}

dormitories %>% view()
```

## Plotting dormitory locations on tmap
```{r}
dormitories_points <- st_as_sf(dormitories, coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(3414)
```

```{r}
dorms_fix_encoding <- dormitories_points %>% 
  mutate(dormitory = iconv(dormitory, to = "UTF-8", sub = ""))
```

```{r}
tmap_mode("view")
```

```{r}
tm_shape(dorms_fix_encoding) + tm_dots()
```

# Grocery shops locations
```{r}
grocery_shops_600m <-  read_csv("data/grocery_shops_locations_test.csv")
```

## Plot on map
```{r}
grocery_shops_600m_points <- st_as_sf(grocery_shops_600m, coords = c("Lon", "Lat"), crs = 4326) %>%
  st_transform(3414)
```

```{r}
#Little India grocery shops we sampled
grocery_shops_points_little_india <- grocery_shops_600m_points %>%
  filter (Remarks == "Little India")
```

```{r}
#Grocery shops near dorms we sampled
grocery_shops_600m_points_dorms <- grocery_shops_600m_points %>%
  filter (Remarks != "Little India")
```

```{r}
### Plot on map
tm_shape(dorms_fix_encoding) + tm_bubbles() + tm_shape(grocery_shops_600m_points_dorms) + tm_dots(col = "blue") + tm_shape(grocery_shops_600m_points_little_india) + tm_dots(col = "purple")
```

## Supermarkets location (NTUC, ShengSiong, Giant)

```{r}
supermarket_locations_filtered <- read.csv("data/supermarket_locations_filtered.csv")
```

```{r}
supermarket_locations_points <- st_as_sf(supermarket_locations_filtered, coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(3414)
```

```{r}
supermarket_locations_points %>%
  tm_shape() + tm_dots()
```

### Visually dorms with supermarkets within 2km

```{r}
supermarkets_2km <- supermarket_locations_points %>%
  st_buffer(2000)
```

```{r}
st_crs(supermarkets_2km)
```

```{r}
st_crs(supermarkets_2km) <- 3414
```

```{r}
supermarkets_2km <- supermarkets_2km %>%
  st_union()
```

```{r}
dorms_supermarkets_2km <- dorms_fix_encoding %>% 
  filter(st_intersects(supermarkets_2km, dorms_fix_encoding, sparse = F)) 
```

```{r}
#green = those with supermarkets within 2km
tm_shape(dorms_fix_encoding) + tm_dots (col = "red") + tm_shape(dorms_supermarkets_2km) + tm_dots (col = "green")
```

### Supermarkets within 2km of dorm

```{r}
dorms_2km <- dorms_fix_encoding %>%
  st_buffer(2000)
```

```{r}
st_crs(dorms_2km)
```

```{r}
st_crs(dorms_2km) <- 3414
```

```{r}
dorms_2km <- dorms_2km %>%
  st_union()
```

```{r}
supermarkets_within_2km_of_dorms <- supermarket_locations_points %>% 
  filter(st_intersects(dorms_2km, supermarket_locations_points, sparse = F)) 
```

```{r}
tm_shape(dorms_fix_encoding) + tm_dots (col = "black") + tm_shape(supermarkets_within_2km_of_dorms) + tm_dots (col = "green")
```

## Plotting all grocery shops around dorms

```{r}
tm_shape(dorms_fix_encoding) + tm_bubbles () + tm_shape(supermarkets_within_2km_of_dorms) + tm_dots (col = "green") + tm_shape(grocery_shops_600m_points_dorms) + tm_dots(col = "blue") + tm_shape(grocery_shops_600m_points_little_india) + tm_dots(col = "purple")
```

# Food outlets locations

```{r}
food_outlets_600m <- read.csv("data/food_outlets_locations_test.csv")
```

```{r}
food_outlets_600m_points <- st_as_sf(food_outlets_600m, coords = c("Lon", "Lat"), crs = 4326) %>%
  st_transform(3414)
```

```{r}
#Little India grocery shops we sampled
food_outlets_points_little_india <- food_outlets_600m_points %>%
  filter (Remarks == "Little India")
```

```{r}
#Grocery shops near dorms we sampled
food_outlets_600m_points_dorms <- food_outlets_600m_points %>%
  filter (Remarks != "Little India") %>%
  filter (Remarks != "Hawker Centre")
```

```{r}
### Plot on map
tm_shape(dorms_fix_encoding) + tm_bubbles() + tm_shape(food_outlets_600m_points_dorms) + tm_dots(col = "blue") + tm_shape(food_outlets_600m_points_little_india) + tm_dots(col = "purple")
```

## Hawker Centres 

```{r}
hawker_centres_locations <- read.csv("data/hawker_centres_locations_cleaned.csv")
```

```{r}
hawker_centres_points <- st_as_sf(hawker_centres_locations, coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(3414)
```

## Visually dorms with hawker centres within 2km

```{r}
HC_2km <- hawker_centres_points %>%
  st_buffer(2000)
```

```{r}
st_crs(HC_2km)
```

```{r}
st_crs(HC_2km) <- 3414
```

```{r}
HC_2km <- HC_2km %>%
  st_union()
```

```{r}
dorms_HC_2km <- dorms_fix_encoding %>% 
  filter(st_intersects(HC_2km, dorms_fix_encoding, sparse = F)) 
```

```{r}
#green = those with hawker centres within 2km
tm_shape(dorms_fix_encoding) + tm_dots (col = "red") + tm_shape(dorms_HC_2km) + tm_dots (col = "green")
```

### Hawker Centres within 2km of dorm

```{r}
HC_within_2km_of_dorms <- hawker_centres_points %>% 
  filter(st_intersects(dorms_2km, hawker_centres_points, sparse = F)) 
```

```{r}
tm_shape(dorms_fix_encoding) + tm_dots (col = "black") + tm_shape(HC_within_2km_of_dorms) + tm_dots (col = "green")
```

## Plotting all food outlets around dorms

```{r}
tm_shape(dorms_fix_encoding) + tm_bubbles () + tm_shape(HC_within_2km_of_dorms) + tm_dots (col = "green") + tm_shape(food_outlets_600m_points_dorms) + tm_dots(col = "blue") + tm_shape(food_outlets_points_little_india) + tm_dots(col = "purple")
```

# Bus stop information
```{r}
bus_stops <-read_sf("data/BusStopLocation_Apr2019/BusStop.shp")
```

```{r}
bus_stops %>%
  tm_shape () + tm_dots()
```

## Dormitories with bus stops within 600m

```{r}
bus_stops_600m <- bus_stops %>%
  st_buffer(600)
```

```{r}
st_crs(bus_stops_600m)
```

```{r}
st_crs(bus_stops_600m) <- 3414
```

```{r}
bus_stops_600m <- bus_stops_600m %>%
  st_union()
```

```{r}
dorms_bus_stops_600m <- dorms_fix_encoding %>% 
  filter(st_intersects(bus_stops_600m, dorms_fix_encoding, sparse = F)) 
```

```{r}
#green = those with bus stops 
tm_shape(dorms_fix_encoding) + tm_dots (col = "red") + tm_shape(dorms_bus_stops_600m) + tm_dots (col = "green")
```

## Bus Stops within 600m of dorms

```{r}
dorms_600m <- dorms_fix_encoding %>%
  st_buffer(600)
```

```{r}
st_crs(dorms_600m)
```

```{r}
st_crs(dorms_600m) <- 3414
```

```{r}
st_crs(bus_stops) <- 3414
```

```{r}
dorms_600m <- dorms_600m %>%
  st_union()
```

```{r}
bus_stops_within_600m_of_dorms <- bus_stops %>% 
  filter(st_intersects(dorms_600m, bus_stops, sparse = F)) 
```

```{r}
#green = those with bus stops 
tm_shape(dorms_fix_encoding) + tm_bubbles () + tm_shape(bus_stops_within_600m_of_dorms) + tm_dots (col = "blue")
```

