---
title: "Analysing Regional Trends in Density of Amenities"
author: "Hayley Garment"
date: "4/24/2020"
output: html_document
---

In this file:
1. Visualize density of bus stops per region and dorm
2. Visualize density of grocery shops per region
3. Visualize density of restaurants per region
4. Visualize density of supermarkets per region
5. Get density of hawker centers per region


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(googlesheets4)
library(janitor)
library(lubridate) # this package is part of tidyverse but not loaded by default
library(repurrrsive)
library(tools)

library(tmap)
library(sf)
library(geojsonsf)
library(ggmap)
library(mapview)
library(sp)

library(httr)
library(osmdata)
library(dplyr)
library(stringr)

library(forcats)
library(infer)
```

```{r}
# read in regional data
sf_regions <- readRDS('data/geo_regions.rds')
dorms <- readRDS('data/dorm_regions.rds')
sf_dorms <- st_as_sf(dorms, crs=3414)
```

1. Visualize bus stops per dorm
```{r}
bus_stops <- readRDS('data/geo_bus_stops_with_ids.rds')

bus_stops_per_dorm <- bus_stops %>% 
  st_set_geometry(NULL) %>%
  group_by(dorm_id) %>% 
  summarize(n_bus_stops = n()) %>% 
  ungroup()

sf_stops_per_dorm <- left_join(sf_dorms, bus_stops_per_dorm)

saveRDS(sf_stops_per_dorm, 'data/calculated/geo_dorm_bus_stops.rds')

tm_shape(sf_stops_per_dorm) +
  tm_dots(col='n_bus_stops', size = 0.07)
```

1. Visualize the density of bus stops in each region
```{r}
# number of dorms and number of stops in each region
dorms_stops_per_region <- left_join(dorms, bus_stops_per_dorm) %>%
  mutate(n_bus_stops = ifelse(is.na(n_bus_stops),0, n_bus_stops)) %>% 
  group_by(region) %>% 
  summarize(regional_bus_stops= sum(n_bus_stops), regional_dorms = n()) %>% 
  ungroup()

# calculate density
dorms_stops_per_region <- dorms_stops_per_region %>%
  mutate(stops_per_dorm = regional_bus_stops/regional_dorms)

sf_regions_with_bus_stops <- left_join(sf_regions, dorms_stops_per_region)

# map
sf_regions_with_bus_stops %>% 
  tm_shape() + 
  tm_polygons(col = 'stops_per_dorm', alpha = 0.5) +
  tm_shape(sf_dorms) +
  tm_dots()

saveRDS(sf_regions_with_bus_stops,  'data/calculated/geo_region_bus_stops.rds')
```

Conclusion: Those two top dorms in west 4 probably sould be in  west 2! Update clusters?

2. Visualize grocery shops per dorm
```{r}
sf_groceries <- readRDS('data/geo_groceries_with_ids.rds')

groceries_per_dorm <- sf_groceries %>% 
  st_set_geometry(NULL) %>%
  group_by(dorm_id) %>% 
  summarize(n_groceries = n()) %>% 
  ungroup()

sf_groceries_per_dorm <- left_join(sf_dorms, groceries_per_dorm)

saveRDS(sf_groceries_per_dorm, 'data/calculated/geo_dorm_groceries.rds')

tm_shape(sf_groceries_per_dorm) +
  tm_dots(col='n_groceries', size = 0.07)
```

2. Visualize grocery shop density per region
```{r}
# number of dorms and number of groceries in each region
dorms_groceries_per_region <- left_join(dorms, groceries_per_dorm) %>%
  mutate(n_groceries = ifelse(is.na(n_groceries),0, n_groceries)) %>% 
  group_by(region) %>% 
  summarize(regional_groceries = sum(n_groceries), regional_dorms = n()) %>% 
  ungroup()

# calculate density
dorms_groceries_per_region <- dorms_groceries_per_region %>%
  mutate(groceries_per_dorm = regional_groceries/regional_dorms)

sf_regions_with_groceries <- left_join(sf_regions, dorms_groceries_per_region)

# map
sf_regions_with_groceries %>% 
  tm_shape() + 
  tm_polygons(col = 'groceries_per_dorm', alpha = 0.5) +
  tm_shape(sf_dorms) +
  tm_dots()

saveRDS(sf_regions_with_groceries,  'data/calculated/geo_region_groceries.rds')
```

Is all of this data  correct? Why would a centrally located dorm not have as many groceries? Need a  way to represent missing data!


3. Visualize restaurants per dorm
```{r}
sf_restaurants <- readRDS('data/geo_restaurants_with_ids.rds')

restaurants_per_dorm <- sf_restaurants %>% 
  st_set_geometry(NULL) %>%
  group_by(dorm_id) %>% 
  summarize(n_restaurants = n()) %>% 
  ungroup()

sf_restaurants_per_dorm <- left_join(sf_dorms, restaurants_per_dorm)

saveRDS(sf_restaurants_per_dorm, 'data/calculated/geo_dorm_restaurants.rds')

tm_shape(sf_restaurants_per_dorm) +
  tm_dots(col='n_restaurants', size = 0.07)
```

3. Visualize restaurant density per region
```{r}
# number of dorms and number of groceries in each region
dorms_restaurants_per_region <- left_join(dorms, restaurants_per_dorm) %>%
  mutate(n_restaurants = ifelse(is.na(n_restaurants),0, n_restaurants)) %>% 
  group_by(region) %>% 
  summarize(regional_restaurants = sum(n_restaurants), regional_dorms = n()) %>% 
  ungroup()

# calculate density
dorms_restaurants_per_region <- dorms_restaurants_per_region %>%
  mutate(restaurants_per_dorm = regional_restaurants/regional_dorms)

sf_regions_with_restaurants <- left_join(sf_regions, dorms_restaurants_per_region)

# map
sf_regions_with_restaurants %>% 
  tm_shape() + 
  tm_polygons(col = 'restaurants_per_dorm', alpha = 0.5) +
  tm_shape(sf_dorms) +
  tm_dots()

saveRDS(sf_regions_with_restaurants,  'data/calculated/geo_region_restaurants.rds')
```

Again, need a way to tag missing data.

4. Visualize supermarkets:(
```{r}
sf_supermarkets <- readRDS('data/geo_supermarkets_2km_with_ids.rds')

supermarkets_per_dorm <- sf_supermarkets %>% 
  st_set_geometry(NULL) %>%
  group_by(dorm_id) %>% 
  summarize(n_supermarkets = n()) %>% 
  ungroup()

sf_supermarkets_per_dorm <- left_join(sf_dorms, supermarkets_per_dorm)

saveRDS(sf_supermarkets_per_dorm, 'data/calculated/geo_dorm_supermarkets.rds')

tm_shape(sf_supermarkets_per_dorm) +
  tm_dots(col='n_supermarkets', size = 0.07)
```

4. Visualize supermarket density per region
```{r}
# number of dorms and number of groceries in each region
dorms_supermarkets_per_region <- left_join(dorms, supermarkets_per_dorm) %>%
  mutate(n_supermarkets = ifelse(is.na(n_supermarkets),0, n_supermarkets)) %>% 
  group_by(region) %>% 
  summarize(regional_supermarkets = sum(n_supermarkets), regional_dorms = n()) %>% 
  ungroup()

# calculate density
dorms_supermarkets_per_region <- dorms_supermarkets_per_region %>%
  mutate(supermarkets_per_dorm = regional_supermarkets/regional_dorms)

sf_regions_with_supermarkets <- left_join(sf_regions, dorms_supermarkets_per_region)

# map
sf_regions_with_supermarkets %>% 
  tm_shape() + 
  tm_polygons(col = 'supermarkets_per_dorm', alpha = 0.5) +
  tm_shape(sf_dorms) +
  tm_dots()

saveRDS(sf_regions_with_supermarkets,  'data/calculated/geo_region_supermarkets.rds')
```


5. Visualize hawkers:(
```{r}
sf_hawkers <- readRDS('data/geo_hawkers_2km_with_ids.rds')

hawkers_per_dorm <- sf_hawkers %>% 
  st_set_geometry(NULL) %>%
  group_by(dorm_id) %>% 
  summarize(n_hawkers = n()) %>% 
  ungroup()

sf_hawkers_per_dorm <- left_join(sf_dorms, hawkers_per_dorm)

saveRDS(sf_hawkers_per_dorm, 'data/calculated/geo_dorm_hawkers.rds')

tm_shape(sf_hawkers_per_dorm) +
  tm_dots(col='n_hawkers', size = 0.07)
```

5. Visualize hawker density per region
```{r}
# number of dorms and number of groceries in each region
dorms_hawkers_per_region <- left_join(dorms, hawkers_per_dorm) %>%
  mutate(n_hawkers = ifelse(is.na(n_hawkers),0, n_hawkers)) %>% 
  group_by(region) %>% 
  summarize(regional_hawkers = sum(n_hawkers), regional_dorms = n()) %>% 
  ungroup()

# calculate density
dorms_hawkers_per_region <- dorms_hawkers_per_region %>%
  mutate(hawkers_per_dorm = regional_hawkers/regional_dorms)

sf_regions_with_hawkers <- left_join(sf_regions, dorms_hawkers_per_region)

# map
sf_regions_with_hawkers %>% 
  tm_shape() + 
  tm_polygons(col = 'hawkers_per_dorm', alpha = 0.5) +
  tm_shape(sf_dorms) +
  tm_dots()

saveRDS(sf_regions_with_hawkers,'data/calculated/geo_region_hawkers.rds')
```