---
title: "Calculating Mean Basket Prices"
author: "Hayley Garment"
date: "4/25/2020"
output: html_document
---

In this file:

1. Calculate mean basket price for each dorm 
2. Calculate mean basket price for each region
3. Get the list of dorms for which there is price data
4. Calculate mean basket price for clustered dorms
5. Summing access in different regions


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(googlesheets4)
library(janitor)
library(lubridate) # this package is part of tidyverse but not loaded by default
library(repurrrsive)
library(tools)

library(tmap)
library(sf)
library(geojsonsf)
library(ggmap)
library(mapview)

library(httr)
library(osmdata)
library(dplyr)
library(stringr)

library(forcats)
library(infer)
```

1. Calculate mean basket price for each dorm 
```{r}
# get grocery shops near each dorm
groceries_dorm_id  <- readRDS('data/geo_groceries_with_ids.rds')
grocery_shops_prices <- read.csv("data/grocery_shops_price_test.csv")

sf_grocery_prices <- left_join(groceries_dorm_id, grocery_shops_prices) %>% 
  select(Shop, dorm_id, Basket.price, geometry)

sf_grocery_prices_no_na <- sf_grocery_prices %>% 
  filter(!is.na(Basket.price))

sf_avg_price_near_dorm <- sf_grocery_prices_no_na %>% group_by(dorm_id) %>% 
  summarize(mean_price = mean(Basket.price)) %>% 
  ungroup()

saveRDS(sf_avg_price_near_dorm,'data/geo_avg_basket_per_dorm.rds')

tm_shape(sf_avg_price_near_dorm) + tm_dots(col='mean_price')
```

2. Calculate mean basket price for each region
```{r}
sf_avg_price_near_dorm <- readRDS('data/geo_avg_basket_per_dorm.rds')
dorm_regions <- readRDS('data/dorm_regions.rds') %>% select(-geometry)
sf_regions  <- readRDS('data/geo_regions.rds')

price_per_dorm_with_region <- left_join(sf_avg_price_near_dorm, dorm_regions)
price_per_region <- price_per_dorm_with_region %>% 
  group_by(region) %>% 
  summarise(mean_price = mean(mean_price)) %>% 
  ungroup() %>% st_set_geometry(NULL)

sf_price_per_region <- left_join(price_per_region, sf_regions) %>% st_as_sf(., crs=3414)
  
saveRDS(sf_price_per_region, 'data/geo_price_per_region.rds')
tm_shape(sf_price_per_region) + tm_polygons(col = 'mean_price')

```


3. Getting the list of dorms for which there is price data
```{r}
geo_prices <- sf_grocery_prices %>% st_set_geometry(NULL)

dorms_with_baskets <- geo_prices %>% filter(!is.na(Basket.price)) %>% distinct(dorm_id)
saveRDS(dorms_with_baskets, 'data/tbl_dorms_with_baskets.rds')


sf_dorms <- readRDS('data/geo_dorms.rds')

dorms_with_baskets <- dorms_with_baskets %>% mutate(has_basket = TRUE)
dorms_with_basket_info <- left_join(sf_dorms, dorms_with_baskets) %>%
  mutate(has_basket = ifelse(is.na(has_basket), FALSE, TRUE))

saveRDS(dorms_with_basket_info, 'data/geo_dorms_has_basket.rds')
```

4. Getting mean price per k means cluster
```{r}
dorm_k_means_clustering <- readRDS('data/geo_k_means_dorms.rds')
regions <- readRDS('data/geo_regions.rds')
avg_price_near_dorm <- readRDS('data/geo_avg_basket_per_dorm.rds') %>% st_set_geometry(NULL)

dorm_k_means_clustering <- dorm_k_means_clustering %>%
  select(-n_hawkers, -n_supermarkets, -n_bus_stops) %>% rename(access_type = .cluster)

dorm_k_means_clustering$access_type <- recode(dorm_k_means_clustering$access_type, `2` = 'Moderate Access', `1` = 'Best Access', `3` = 'Poor Access')

prices_per_dorm_with_access_type <- left_join(dorm_k_means_clustering, avg_price_near_dorm) %>% filter(!is.na(mean_price))

price_per_access_type <- prices_per_dorm_with_access_type %>% 
  group_by(access_type) %>% 
  summarise(mean_price = mean(mean_price)) %>% 
  ungroup()

saveRDS(dorm_k_means_clustering, 'data/geo_dorms_with_access_clusters.rds')
saveRDS(price_per_access_type, 'data/tbl_price_per_access_type.rds')
```

5. Summing access in different regions
```{r}
regions_by_access <- left_join(dorm_k_means_clustering, dorm_regions) %>%  group_by(region) %>% 
  summarise(perc_poor_access = sum(access_type == 'Poor Access')/n(),
            perc_mod_access = sum(access_type == 'Moderate Access')/n(),
            perc_best_access =  sum(access_type == 'Best Access')/n(),) %>% 
  ungroup()

sf_regions_by_access <- left_join(regions_by_access, regions) %>% st_as_sf(., crs=3414)

saveRDS(sf_regions_by_access, 'data/geo_regions_by_access.rds')
tm_shape(sf_regions_by_access) + tm_polygons(col='perc_best_access')
tm_shape(sf_regions_by_access) + tm_polygons(col='perc_poor_access')
```

