---
title: "Visualizing Price Distribution"
author: "Hayley Garment"
date: "4/20/2020"
output: html_document
---

# Visualizing Distribution of Food Prices around Migrant Worker Dormitories

**Table of Contents**
1. Visualize Dorms
2. Visualize Regions
3. Visualize Amenities
4. Visualize Amenities nearby Dorms

5. Visualize Price per basket per Dorm and Region
7. Visualize Price per PCA clusters

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

library(tmap)
library(sf)
library(geojsonsf)
library(ggmap)
library(mapview)

library(httr)
library(osmdata)
library(dplyr)
library(stringr)

library(forcats)
library(infer)
```

Colors
```{r}
blue <- '#63eaff'
purple <- '#6375ff'
red <- '#e06e6e'
green <- '#8ce06e'
yellow <- '#ffe100'
```


1. Visualize Dorms
```{r}
tmap_mode("view")
sf_dorms <- readRDS('data/geo_dorms_has_basket.rds')

dorms_no_basket<- sf_dorms %>% filter(has_basket==FALSE)

tm_shape(sf_dorms) + tm_dots(col=red) +
  tm_shape(dorms_no_basket) + tm_dots(col ='grey') +
  tm_add_legend (
    type = "fill",
    labels = c('has price data', 'no price data'),
    col = c(red, 'grey'))
```

2. Visualize Regions
```{r}
sf_regions <- readRDS('data/geo_regions.rds')
sf_regions %>% count()

tm_shape(sf_regions) + tm_polygons(alpha=0.5, col='region', palette = "Paired", n = 13, legend.show=FALSE) +
  tm_shape(sf_dorms) + tm_dots()
```

3. Visualize Amenities
```{r}
supermarkets <- readRDS('data/geo_supermarkets.rds')
hawkers <- readRDS('data/geo_hawkers.rds')
bus_stops <- readRDS('data/geo_bus_stops.rds')

tm_shape(bus_stops) + tm_dots(col=purple, size=0.005) +
tm_shape(supermarkets) + tm_dots(col=green, size = 0.03) +
tm_shape(hawkers) + tm_dots(col=red, size = 0.03) +
tm_shape(sf_dorms) + tm_dots(col=yellow, size = 0.06) +
tm_layout(title='Official Dorms, Supermarkets, Hawker Centers and Bus Stops') +
tm_add_legend (
    type = "fill",
    labels = c('dormitory', 'supermarket', 'hawker center', 'bus stop'),
    col = c(yellow, green, red, purple),
    title = "")

```

4.Visualize Amenities near dorms
```{r}
nearby_hawkers <- readRDS('data/geo_hawkers_2km_with_ids.rds')
nearby_supermarkets <- readRDS('data/geo_supermarkets_2km_with_ids.rds')
nearby_bus_stops <- readRDS('data/geo_bus_stops_with_ids.rds') %>% st_transform(crs=3414)

tm_shape(nearby_bus_stops) + tm_dots(col=purple, size=0.005) +
tm_shape(nearby_supermarkets) + tm_dots(col=green, size = 0.03) +
tm_shape(nearby_hawkers) + tm_dots(col=red, size = 0.03) +
tm_shape(sf_dorms) + tm_dots(col=yellow, size = 0.04) +
tm_layout(title='Nearby Supermarkets, Hawker Centers and Bus Stops') +
tm_add_legend (
    type = "fill",
    labels = c('dormitory', 'supermarket', 'hawker center', 'bus stop'),
    col = c(yellow, green, red, purple),
    title = "")
```


5. Visualize Mean Basket Price per Dorm and Region
```{r}
avg_basket_dorm <- readRDS('data/geo_avg_basket_per_dorm.rds')
tm_shape(avg_basket_dorm) + tm_dots(col='mean_price')

avg_basket_region <- readRDS('data/geo_price_per_region.rds')
tm_shape(avg_basket_region) + 
    tm_polygons(col='mean_price',
                palette = "viridis", n = 5, contrast = c(0.9, 0.7),
                alpha = 0.5,
                legend.format = list(fun = function(x) paste0('$', x))) +
  tm_shape(avg_basket_dorm) + tm_dots() +
  tm_shape(dorms_no_basket) + tm_dots() +
  tm_layout(title='Mean Price of Basket of Goods by Region')
```






```{r}
mrt_lines_sf <- readRDS('data/lines_sf.rds')
dorms_with_access_clusters <- readRDS( 'data/geo_dorms_with_access_clusters.rds') %>% st_as_sf(., crs=3414)

best_access <- dorms_with_access_clusters %>% filter(access_type == 'Best Access')
mod_access <- dorms_with_access_clusters %>% filter(access_type == 'Moderate Access')
poor_access <- dorms_with_access_clusters %>% filter(access_type == 'Poor Access')

tm_shape(best_access) + tm_dots(col=blue) +
tm_shape(mod_access) + tm_dots(col=yellow) +
tm_shape(poor_access) + tm_dots(col=red)

regions_with_access <- readRDS('data/geo_regions_by_access.rds') %>% mutate()

tm_shape(best_access) + tm_dots(col=blue) +
tm_shape(mod_access) + tm_dots(col=yellow) +
tm_shape(poor_access) + tm_dots(col=red) +
    tm_shape(mrt_lines_sf) + 
tm_lines(col = "colour") +
  tm_layout(title='Dorms by Access Category') +
  tm_add_legend (
    type = "fill",
    labels = c('best access - $37.9/bskt', 'moderate acccess - $35.0/bskt', 'poor access - $34.4/bskt'),
    col = c(blue, yellow, red),
    title='Mean Price per Access Category')

tm_shape(regions_with_access) + 
  tm_polygons(col='perc_poor_access',
              palette = "plasma", n = 6, contrast = c(0.5, 0.0),
              alpha = 0.4) +
  tm_shape(mrt_lines_sf) + 
tm_lines(col = "colour") +
  tm_layout(title='Regions by Percent of Dorms with Poor Access')
```


```{r}
price_acesss_per_region <- st_join(avg_basket_region, regions_with_access) %>% select(region.x, mean_price, perc_best_access)

ggplot(price_acesss_per_region, aes(perc_best_access, mean_price)) + geom_point()

cor(price_acesss_per_region$mean_price, price_acesss_per_region$perc_best_access, method = "pearson")

lm(price_acesss_per_region$mean_price ~  price_acesss_per_region$perc_best_access)
```

